### 2019-05-22 2-Chapters/3-Chapter/chapter3.tex
So long
Small proofreading of notations of Chapter6

For Cognitive Radio dealing with OSA problems and other applications, a well-studied extension is to consider $M\geq2$ players, interacting on the same $K$ arms.
Whenever two or more players select the same arm at the same time (\eg, for OSA, the same frequency channel), they all suffer from a radio collision.
%
Different collision models have been proposed, and the simplest one consists in giving a $0$ reward to each colliding players.
Without any centralized supervision or coordination between players, they must learn to access the $M$ best resources (\ie, arms with highest means) without collisions.
We refer to Chapter~\ref{chapter:5} which introduces and details various multi-player bandit models.

@@

Finally, the most exciting thing that could happen to our SMPyBandits library would be to see it gaining popularity!
Its documentation has seen already about $20000$ visits, the project on GitHub had $76$ stars in June $2019$, and based on the features requested and the emails received about it, we counted between $15$ to $25$ researchers in other labs we use or used SMPyBandits.
While this is a good start, we believe that the library is mature and interesting enough to hope to see it being used by more people.
%
We have submitted a summary paper presenting SMPyBandits \cite{SMPyBanditsJMLR} to the MLOSS track of the Journal of Machine Learning Research (JMLR), and we hope to be accepted, as it would give more visibility to our work.\\
%
\indent
As a personal note, I would like to continue working on SMPyBandits, and implement the most important requested features, as well as maintain it, and possibly continue to add recent algorithms by following actively the research in this community.
I would also love to be able in the next to teach a graduate or under-graduate course on multi-armed bandits, and use my library as a support to illustrate the course, as well as practical sessions.

>>>>

For Cognitive Radio dealing with OSA problems and other applications, a well-studied extension is to consider $M\geq2$ players, interacting on the same $K$ arms.
Whenever two or more players select the same arm at the same time (\eg, for OSA, the same frequency channel), they all suffer from a radio collision.
%
Different collision models have been proposed, and the simplest one consists in giving a $0$ reward to each colliding players.
Without any centralized supervision or coordination between players, they must learn to access the $M$ best resources (\ie, arms with highest means) without collisions.
We refer to Chapter~\ref{chapter:5} which introduces the multi-player bandit model.

@@

Finally, the most exciting thing that could happen to our SMPyBandits library would be to see it gaining popularity!
Its documentation has seen already about $20000$ visits, the project on GitHub had $85$ stars in June $2019$, and based on the features requested and the emails received about it, we counted between $15$ to $25$ researchers in other labs we use or used SMPyBandits.
While this is a good start, we believe that the library is mature and interesting enough to hope to see it being used by more people.
%
We have submitted a summary paper presenting SMPyBandits \cite{SMPyBanditsJMLR} to the MLOSS track of the Journal of Machine Learning Research (JMLR), and we hope to be accepted, as it would give more visibility to our work.\\
%
\indent
As a personal note, I would like to continue working on SMPyBandits, and implement the most important requested features, as well as maintain it, and possibly continue to add recent algorithms by following actively the research in this community.
I would also love to be able in the next to teach a graduate or under-graduate course on multi-armed bandits, and use my library as a support to illustrate the course, as well as practical sessions.

### 2019-05-22 2-Chapters/6-Chapter/nonstatbandits.git/NonStatB.tex
Small proofreading of notations of Chapter6

\TODOL{Okay ça suffit pour ces travaux ?}

@@

Assume that we collect independent samples $X_1,X_2,\ldots$ all from some distribution supported in $[0,1]$.
We want to discriminate between two possible scenarios: all the samples come from distributions that have a common mean $\mu_0$, or there exists a \emph{change-point} $\tau > 1$ such that $X_1,\ldots,X_\tau$ have some mean $\mu_0$ and $X_{\tau +1},X_{\tau+2},\ldots$ have a different mean $\mu_1 \neq \mu_0$.
%
A sequential change-point detector is a stopping time $\widehat{\tau}$ with respect to the filtration $\cF_t = \sigma(X_1,\dots,X_t)$ such that $(\hat \tau < \infty)$ means that we reject the hypothesis
$\cH_0 : \left(\exists \mu_0 \in [0,1]: \forall i\in\N^*, \bE[X_i] = \mu_0\right)$.

@@

Lemma~1 of \cite{KLUCBJournal} establishes that any bounded distribution supported in $[0,1]$ is a sub-Bernoulli distribution.
Our work can be applied to any bounded distribution without loss of generality, as a reward in $r\in[a,b]$ can clearly be mapped to $[0,1]$ simply by using $r' = (r-a)/(b-a)$ (we assume that the decision maker or the algorithm know before hand the values of $a,b$).

@@

\begin{proof}
    First, we consider the denominator in the expression of $\GLR(n)$ \eqref{eq:6:firstDefGLRT}, that is the $\sup$ on $\mu_0$.
    We have $\ell(X_1, \ldots, X_n ; \mu_0) = \prod_{i=1}^n \ell(X_i ; \mu_0)$ by independence of the observations $X_i$,
    and $\ell(X_i ; \mu_0) = \mu_0^{X_i} (1-\mu_0)^{1-X_i}$ for Bernoulli distributions.
    Therefore, taking the logarithm gives
    \begin{align*}
        \log\ell(X_1, \ldots, X_n ; \mu_0)
        &= \sum_{i=1}^n X_i \log(\mu_0) + (1-X_i) \log(1-\mu_0) \\
        &= \log(\mu_0) \times \left( \sum_{i=1}^n X_i \right) + \log(1-\mu_0) \times \left( n - \sum_{i=1}^n X_i \right) \\
        &= n \left[ \widehat{\mu}_{1:n} \log(\mu_0) + (1 - \widehat{\mu}_{1:n}) \log(1-\mu_0) \right].
    \end{align*}
    %
    For a constant $a\in[0,1]$, let $h(x) := a \log(x) + (1-a) \log(1-x)$ on $(0,1)$,
    and we are trying to solve $\sup_{x\in[0,1]} h(x)$.
    If $a=0$ or $a=1$, $h$ is maximum at $x=a$.
    Now if $a\neq0$, As $h$ is of class $\cC^1$, we can just differentiate and find the root of its derivative:
    $h'(x) = a/x - (1-a)/(1-x)$, so $h'(x) = 0$ if and only if $x=a$.
    Thus in all cases, $\sup_{x\in[0,1]} h(x) = h(a)$.
    %
    Here, we have $a = \widehat{\mu}_{1:n}$, and thus we solve the $\sup_{\mu_0}$ optimization problem found in the denominator of the $\GLR(n)$ expression.
    By replacing $\mu_0 = \widehat{\mu}_{1:n}$, we obtained the following (unique) solution,
    \begin{equation}\label{eq:6:solutionPbOpt_for_1n}
        \sup_{\mu_0} \log\ell(X_1, \ldots, X_n ; \mu_0) = n \left( \widehat{\mu}_{1:n} \log(\widehat{\mu}_{1:n}) + (1 - \widehat{\mu}_{1:n}) \log(1-\widehat{\mu}_{1:n}) \right).
    \end{equation}

@@

        &= \exp \Bigl[ \sup\limits_{\mu_0,\mu_1,\tau < n} \Bigl[ \log\Bigl[ \frac{\ell(X_1, \ldots, X_n ; \mu_0,\mu_1,\tau)}{ \exp\left[ n \left( \widehat{\mu}_{1:n} \log(\widehat{\mu}_{1:n}) + (1 - \widehat{\mu}_{1:n}) \log(1-\widehat{\mu}_{1:n}) \right) \right] } \Bigr] \Bigr] \Bigr],  \\
        &= \exp \Bigl[ \sup\limits_{\mu_0,\mu_1, 1 < s < n} \Bigl[

@@

        \Bigr] \Bigr].

@@

        = \exp \Bigl[ \sup\limits_{1 < s < n} \Bigl[

@@

\begin{lemma}\label{lem:6:Delay}
    Let be $\bP_{\mu_0,\mu_1,\tau}$ a probabilistic model under which $X_t \in [0,1]$, and $X_t$ has an average of $\mu_0$ for all $t \leq \tau$, and $\mu_1$ for all $t > \tau$, with $\mu_0 \neq \mu_1$,
    and let $\Delta = |\mu_0 - \mu_1|$.
    Then the B-GLRT test given in Definition~\ref{def:6:GLRDef} satisfies
    \begin{equation}
        \bP_{\mu_0,\mu_1,\tau} (\widehat{\tau}_{\delta} \geq \tau + u) \leq \exp\left( -\frac{2\tau u}{\tau + u}\left(\max\left[ 0, \Delta - \sqrt{\frac{\tau + u}{2\tau u} \beta(\tau + u,\delta)} \right]\right)^2 \right).
    \end{equation}
\end{lemma}
%
\begin{proof}
    It is actually not used as such in the proofs of the regret upper bound given below, but a similar result is used and proved in the proofs.
    \TODOL{We have to give the proof, or remove this result? Je ne vois pas le problème de le laisser là, ça formalise le résultat mais on a pas besoin de celui là, ça permet de bien formaliser ce qu'on entend par contrôler le délai, et dans la preuve plus bas on prouve ce qu'on souhaite.}
\end{proof}

@@

This Section starts by giving a unified analysis of regret of the two variants of our algorithm, then we give the proof of the finite-time regret bound for the variant using ``global restarts''.
The proof of the other variant using ``local restarts'' follows the skeleton of the unified analysis, and can be found in Appendix~E of \cite{Besson2019GLRT}.

@@

In this section, we sketch a unified proof for the two Theorems \ref{thm:6:mainRegretBoundGlobal} and \ref{thm:6:mainRegretBound} given below, whose detailed proofs are given in Section~\ref{proof:6:mainRegretBoundGlobal} and in Appendix~E of our paper \cite{Besson2019GLRT} respectively.
We emphasize that our approach is significantly different from those proposed by \cite{CaoZhenKvetonXie18} for \MUCB{} and by \cite{LiuLeeShroff17} for \CUSUMUCB.

Recall that the regret is defined as $R_T = \bE\left[\sum_{t=1}^T(\mu_{i^*_t}(t) - \mu_{I_t}(t))\right]$.
Introducing $\cD(T,\alpha)$ the (deterministic) set of time steps at which the forced exploration is performed before time $T$ (see lines $3$-$4$ in Algorithm~\ref{algo:6:GLRklUCB}),
we observe that we have $\mu_{i^*_t} - \mu_{I_t} \leq 1$ because rewards are assumed to be bounded in $[0,1]$,
and thus we can write a first decomposition of the regret,
\begin{align*}
 & \sum_{t=1}^T (\mu_{i^*_t}(t) - \mu_{I_t}(t)) \\
 & \hspace{1cm} \leq  \sum_{t=1}^{T} \indic(t \in \cD(T,\alpha)) + \sum_{t=1}^T (\mu_{i^*_t}(t) - \mu_{I_t}(t))\indic\left(t \notin\cD(T,\alpha), \UCB_{I_t}(t) \geq \UCB_{i^*_t}(t)\right) \\
 & \hspace{1cm}\leq  \alpha T + \sum_{t=1}^T \indic\left(\UCB_{i^*_t}(t) \leq \mu_{i^*_t}(t)\right) + \sum_{i=1}^K\sum_{t=1}^T (\mu_{i^*_t}(t) - \mu_{i}(t))\indic\left(I_t = i, \UCB_{i}(t) \geq \mu_{i^*_t}(t)\right).
\end{align*}
%
Introducing some \emph{good event} $\cE_T$, to be specified in each case, and its complementary $\cE_T^c$, one can write the following decomposition, that highlights two important terms $(A)$ and $(B)$
%
\begin{align}\label{eq:6:GeneRegretBound}
    R_T \leq T \bP\left(\cE_T^c\right) + \alpha T & + \underbrace{\bE\left[\indic(\cE_T) \sum_{t=1}^T \indic\left(\UCB_{i^*_t}(t) \leq \mu_{i^*_t}(t)\right)\right]}_{(A)} \\
    & + \underbrace{\bE\left[\indic(\cE_T)\sum_{t=1}^T (\mu_{i^*_t}(t) - \mu_{I_t}(t))\indic\left(\UCB_{I_t}(t) \geq \mu_{i^*_t}(t)\right)\right]}_{(B)}. \nonumber
\end{align}
%
Each analysis requires to define an \emph{appropriate good event}, stating that \emph{some} change-points are detected within a reasonable delay. Each regret bound then follows from upper bounds on term $(A)$, term $(B)$, and on the failure probability $\bP(\cE_T^c)$.
%
To control $(A)$ and $(B)$, we split the sum over consecutive segments $[\tau^{(k)}+1, \tau^{(k+1)}]$ for global changes and $[\tau^{(k)}_i+1, \tau^{(k+1)}_i]$ for each arm $i$ for local changes, and use elements from the analysis of \klUCB{} of \cite{KLUCBJournal}.

@@

\paragraph{Upper bound on term $(b)$: controlling the delay.}
%
From the definition of $\Delta^{(k)}$, there exists an arm $i$ such that $\Delta^{(k)} = |\mu_i^{(k)} - \mu_i^{(k-1)}|$. We shall prove that it is unlikely that the change-point detector associated to $i$ doesn't trigger within the delay $d^{(k)}$.

@@

Moreover, due to Proposition~\ref{prop:6:EnoughSamples}, $n_i(\tau^{(k)})$ lies in the interval $
\left[\left\lfloor \frac{\alpha}{K}\left(\tau^{(k)}-\widehat{\tau}^{(k-1)}\right)\right\rfloor,\left(\tau^{(k)}-\widehat{\tau}^{(k-1)}\right)\right]$. Conditionally to $\cC^{(k-1)}$, one obtains furthermore using that $d^{(k-1)} \leq (\tau^{(k)} - \tau^{(k-1)})/2$ -- which follows from Assumption~\ref{ass:6:LongPeriodsGlobal} -- that
%
\begin{eqnarray*}
    n_i(\tau^{(k)})& \in& \left\{ \left\lfloor \frac{\alpha}{2K} (\tau^{(k)}-\tau^{(k-1)} )\right\rfloor, \dots, \tau^{(k)}-\tau^{(k-1)} \right\} := \cI_k.
\end{eqnarray*}

@@

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.00\linewidth]{2-Chapters/6-Chapter/Images/Visualizing_locations_of_change_points_for_different_algorithms__4algs_Pb1.pdf}
    \caption{Location of the detected change-points for four algorithms on Problem 1.}
    \label{fig:6:Visualizing_locations_of_change_points_for_different_algorithms__4algs_Pb1}
\end{figure}

% \TODOL{Conclusion à tirer de cet exemple !}

@@

% \TODOL{Conclusion à tirer de cet exemple !}

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.00\linewidth]{2-Chapters/6-Chapter/Images/Visualizing_locations_of_change_points_for_different_algorithms__4algs_Pb2.pdf}
    \caption{Location of the detected change-points for four algorithms on Problem 2.}
    \label{fig:6:Visualizing_locations_of_change_points_for_different_algorithms__4algs_Pb2}
\end{figure}

@@

On simple problems, like problem $1$, all the algorithms being designed for piece-wise stationary environments perform similarly, but as soon as the gaps are smaller or there is more changes, we clearly observe that our approach \GLRklUCB{} can outperform the two other actively adaptive algorithms \CUSUMklUCB{} and \MklUCB{} (\eg, on Figure~\ref{fig:6:meanRegretPb2}), and performs much more than passively adaptive algorithms DTS and SW-\klUCB{}  (\eg, on Figure~\ref{fig:6:meanRegretPb3}).
Our approach, with the two options of \textbf{Local} or \textbf{Global} restarts, performs very closely to the oracle for problem $4$.

>>>>

% \TODOL{Okay ça suffit pour ces travaux ?}

@@

Assume that we collect independent samples $X_1,X_2,\ldots$ all from some distributions supported in $[0,1]$.
We want to discriminate between two possible scenarios: all the samples come from distributions that have a common mean $\mu_0$, or there exists a \emph{change-point} $\tau > 1$ such that $X_1,\ldots,X_\tau$ have some mean $\mu_0$ and $X_{\tau +1},X_{\tau+2},\ldots$ have a different mean $\mu_1 \neq \mu_0$.
%
A sequential change-point detector is a stopping time $\widehat{\tau}$ with respect to the filtration $\cF_t = \sigma(X_1,\dots,X_t)$ such that $(\hat \tau < \infty)$ means that we reject the hypothesis
$\cH_0 : \left(\exists \mu_0 \in [0,1]: \forall i\in\N^*, \bE[X_i] = \mu_0\right)$.

@@

Lemma~1 of \cite{KLUCBJournal} establishes that any bounded distribution supported in $[0,1]$ is a sub-Bernoulli distribution.
As explained in in Section~\ref{par:2:normalizationTrick}, our work can be applied to any bounded distribution without loss of generality, as a reward in $r\in[a,b]$ can clearly be mapped to $[0,1]$ simply by using $r' = (r-a)/(b-a)$ (we assume that the decision maker or the algorithm knows before hand the values of $a$ and $b$).

@@

\begin{proof}
    First, we consider the denominator in the expression of $\GLR(n)$ \eqref{eq:6:firstDefGLRT}, that is the $\sup$ on $\mu_0$.
    We have $\ell(X_1, \ldots, X_n ; \mu_0) = \prod_{i=1}^n \ell(X_i ; \mu_0)$ by independence of the observations $X_i$,
    and $\ell(X_i ; \mu_0) = \mu_0^{X_i} (1-\mu_0)^{1-X_i}$ for Bernoulli distributions.
    Therefore, taking the logarithm gives
    \begin{align*}
        \log\ell(X_1, \ldots, X_n ; \mu_0)
        &= \sum_{i=1}^n X_i \log(\mu_0) + (1-X_i) \log(1-\mu_0) \\
        &= \log(\mu_0) \times \left( \sum_{i=1}^n X_i \right) + \log(1-\mu_0) \times \left( n - \sum_{i=1}^n X_i \right) \\
        &= n \left( \widehat{\mu}_{1:n} \log(\mu_0) + (1 - \widehat{\mu}_{1:n}) \log(1-\mu_0) \right).
    \end{align*}
    %
    For a constant $a\in[0,1]$, let $h(x) := a \log(x) + (1-a) \log(1-x)$ on $(0,1)$,
    and we are trying to solve $\sup_{x\in[0,1]} h(x)$.
    If $a=0$ or $a=1$, $h$ is maximum at $x=a$.
    Now if $a\neq0$, As $h$ is of class $\cC^1$, we can just differentiate and find the root of its derivative:
    $h'(x) = a/x - (1-a)/(1-x)$, so $h'(x) = 0$ if and only if $x=a$.
    Thus in all cases, $\sup_{x\in[0,1]} h(x) = h(a)$.
    %
    Here, we have $a = \widehat{\mu}_{1:n}$, and thus we solve the $\sup_{\mu_0}$ optimization problem found in the denominator of the $\GLR(n)$ expression.
    By replacing $\mu_0 = \widehat{\mu}_{1:n}$, we obtained the following (unique) solution,
    \begin{equation}\label{eq:6:solutionPbOpt_for_1n}
        \sup_{\mu_0} \log\ell(X_1, \ldots, X_n ; \mu_0) = n \left( \widehat{\mu}_{1:n} \log(\widehat{\mu}_{1:n}) + (1 - \widehat{\mu}_{1:n}) \log(1-\widehat{\mu}_{1:n}) \right).
    \end{equation}

@@

        &= \exp \Bigl[ \sup\limits_{\mu_0,\mu_1,\tau < n} \Bigl[ \log\Bigl[ \frac{\ell(X_1, \ldots, X_n ; \mu_0,\mu_1,\tau)}{ \exp\left[ n \left( \widehat{\mu}_{1:n} \log(\widehat{\mu}_{1:n}) + (1 - \widehat{\mu}_{1:n}) \log(1-\widehat{\mu}_{1:n}) \right) \right] } \Bigr] \Bigr] \Bigr],
    When the last equation comes from the fact that $\exp$ is increasing.
    Thus by taking the logarithm of both sides, we obtain
        \log \GLR(n)
        &= \sup\limits_{\mu_0,\mu_1,\tau < n} \Bigl[ \log\Bigl[ \frac{\ell(X_1, \ldots, X_n ; \mu_0,\mu_1,\tau)}{ \exp\left[ n \left( \widehat{\mu}_{1:n} \log(\widehat{\mu}_{1:n}) + (1 - \widehat{\mu}_{1:n}) \log(1-\widehat{\mu}_{1:n}) \right) \right] } \Bigr] \Bigr],  \\
        &= \sup\limits_{\mu_0,\mu_1, 1 < s < n} \Bigl[

@@

        \Bigr].

@@

        \log \GLR(n)
        = \sup\limits_{1 < s < n} \Bigl[

@@

\begin{lemma}\label{lem:6:Delay}
    Let be $\bP_{\mu_0,\mu_1,\tau}$ a probabilistic model under which $X_t \in [0,1]$, and $X_t$ has an average of $\mu_0$ for all $t \leq \tau$, and $\mu_1$ for all $t > \tau$, with $\mu_0 \neq \mu_1$,
    and let $\Delta = |\mu_0 - \mu_1|$.
    Then the B-GLRT test given in Definition~\ref{def:6:GLRDef} satisfies
    \begin{equation}
        \bP_{\mu_0,\mu_1,\tau} (\widehat{\tau}_{\delta} \geq \tau + u) \leq \exp\left( -\frac{2\tau u}{\tau + u}\left(\max\left[ 0, \Delta - \sqrt{\frac{\tau + u}{2\tau u} \beta(\tau + u,\delta)} \right]\right)^2 \right).
    \end{equation}
\end{lemma}
%
\begin{proof}
    It is actually not used as such in the proofs of the regret upper bounds given below, because a similar but more specific result is used and proved in the proofs.
    For instance, see below in Section~\ref{par:6:controllingDelayInOneProof} in page~\pageref{par:6:controllingDelayInOneProof}.
    % \TODOL{We have to give the proof, or remove this result? Je ne vois pas le problème de le laisser là, ça formalise le résultat mais on a pas besoin de celui là, ça permet de bien formaliser ce qu'on entend par contrôler le délai, et dans la preuve plus bas on prouve ce qu'on souhaite.}
\end{proof}

@@

This Section starts by giving a unified analysis of regret of the two variants of our algorithm, then we give the proof of the finite-time regret bound for the variant using ``global restarts''.
The proof of the other variant using ``local restarts'' follows the skeleton of the unified analysis, and it can be found in Appendix~E of \cite{Besson2019GLRT}.

@@

In this section, we sketch a unified proof for the two Theorems \ref{thm:6:mainRegretBoundGlobal} and \ref{thm:6:mainRegretBound} given above.
%  whose detailed proofs are given in Section~\ref{proof:6:mainRegretBoundGlobal} and in Appendix~E of our paper \cite{Besson2019GLRT} respectively.
We emphasize that our approach is significantly different from those proposed by \cite{CaoZhenKvetonXie18} for \MUCB{} and by \cite{LiuLeeShroff17} for \CUSUMUCB.
%
Recall that in this Chapter, the regret is defined as $R_T = \bE\left[\sum_{t=1}^T(\mu_{i^*_t}(t) - \mu_{I_t}(t))\right]$.
First, we introduce $\cD(T,\alpha)$ the (deterministic) set of time steps at which the forced exploration is performed before time $T$ (see lines $3$-$4$ in Algorithm~\ref{algo:6:GLRklUCB}),
and as we observe that $\mu_{i^*_t} - \mu_{I_t} \leq 1$ because rewards are assumed to be bounded in $[0,1]$,
we can write a first decomposition of the regret,
\begin{align*}
 & \sum_{t=1}^T (\mu_{i^*_t}(t) - \mu_{I_t}(t)) \\
 & \hspace{1cm} \leq  \sum_{t=1}^{T} \indic(t \in \cD(T,\alpha)) + \sum_{t=1}^T (\mu_{i^*_t}(t) - \mu_{I_t}(t))\indic\left(t \notin\cD(T,\alpha), \UCB_{I_t}(t) \geq \UCB_{i^*_t}(t)\right) \\
 & \hspace{1cm}\leq  \alpha T + \sum_{t=1}^T \indic\left(\UCB_{i^*_t}(t) \leq \mu_{i^*_t}(t)\right) + \sum_{i=1}^K\sum_{t=1}^T (\mu_{i^*_t}(t) - \mu_{i}(t))\indic\left(I_t = i, \UCB_{i}(t) \geq \mu_{i^*_t}(t)\right).
\end{align*}
%
Introducing some \emph{good event} $\cE_T$, to be specified in each case, and its complementary $\cE_T^c$, one can write the following decomposition, that highlights two important terms $(A)$ and $(B)$
%
\begin{align}\label{eq:6:GeneRegretBound}
    R_T \leq T \bP\left(\cE_T^c\right) + \alpha T & + \underbrace{\bE\left[\indic(\cE_T) \sum_{t=1}^T \indic\left(\UCB_{i^*_t}(t) \leq \mu_{i^*_t}(t)\right)\right]}_{(A)} \\
    & + \underbrace{\bE\left[\indic(\cE_T)\sum_{t=1}^T (\mu_{i^*_t}(t) - \mu_{I_t}(t))\indic\left(\UCB_{I_t}(t) \geq \mu_{i^*_t}(t)\right)\right]}_{(B)}. \nonumber
\end{align}
%
Each analysis requires to define an \emph{appropriate good event}, stating that \emph{some} change-points are detected within a reasonable delay. Each regret bound then follows from upper bounds on term $(A)$, term $(B)$, and on the failure probability $\bP(\cE_T^c)$.
%
To control $(A)$ and $(B)$, we split the sum over consecutive segments $[\tau^{(k)}+1, \tau^{(k+1)}]$ for global changes and $[\tau^{(k)}_i+1, \tau^{(k+1)}_i]$ for each arm $i$ for local changes, and use elements from the analysis of \klUCB{} of \cite{KLUCBJournal}.

@@

\paragraph{Upper bound on term $(b)$: controlling the delay.}
\label{par:6:controllingDelayInOneProof}
%
From the definition of $\Delta^{(k)}$, there exists an arm $i$ such that $\Delta^{(k)} = |\mu_i^{(k)} - \mu_i^{(k-1)}|$. We shall prove that it is unlikely that the change-point detector associated to $i$ doesn't trigger within the delay $d^{(k)}$.

@@

Moreover, due to Proposition~\ref{prop:6:EnoughSamples}, $n_i(\tau^{(k)})$ lies in the interval $
\left[\left\lfloor \frac{\alpha}{K}\left(\tau^{(k)}-\widehat{\tau}^{(k-1)}\right)\right\rfloor,\left(\tau^{(k)}-\widehat{\tau}^{(k-1)}\right)\right]$.
Conditionally to $\cC^{(k-1)}$,
by using Assumption~\ref{ass:6:LongPeriodsGlobal},
we can prove that $d^{(k-1)} \leq (\tau^{(k)} - \tau^{(k-1)})/2$,
and thus we obtain furthermore that
%
\begin{eqnarray*}
    n_i(\tau^{(k)})& \in& \left\{ \left\lfloor \frac{\alpha}{2K} (\tau^{(k)}-\tau^{(k-1)} )\right\rfloor, \dots, \tau^{(k)}-\tau^{(k-1)} \right\} := \cI_k.
\end{eqnarray*}

@@

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=0.90\linewidth]{2-Chapters/6-Chapter/Images/Visualizing_locations_of_change_points_for_different_algorithms__4algs_Pb1.pdf}
    \caption{Locations of the detected change-points for four algorithms on Problem 1.}
    \label{fig:6:Visualizing_locations_of_change_points_for_different_algorithms__4algs_Pb1}
\end{figure}

@@

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=0.90\linewidth]{2-Chapters/6-Chapter/Images/Visualizing_locations_of_change_points_for_different_algorithms__4algs_Pb2.pdf}
    \caption{Locations of the detected change-points for four algorithms on Problem 2.}
    \label{fig:6:Visualizing_locations_of_change_points_for_different_algorithms__4algs_Pb2}
\end{figure}

@@

On simple problems, like problem $1$, all the algorithms being designed for piece-wise stationary environments perform similarly, but as soon as the gaps are smaller or there are more changes, we clearly observe that our approach \GLRklUCB{} can outperform the two other actively adaptive algorithms \CUSUMklUCB{} and \MklUCB{} (\eg, on Figure~\ref{fig:6:meanRegretPb2}), and performs much better than passively adaptive algorithms DTS and SW-\klUCB{}  (\eg, on Figure~\ref{fig:6:meanRegretPb3}).
% Our approach, with the two options of \textbf{Local} or \textbf{Global} restarts, performs very closely to the oracle for problem $4$.
Our approach is the algorithm which performs the closer to the oracle for problem $4$.
